Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-10 main.tex
pictues on: makespan relations by size, 2 pictures on runtimes

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.495\columnwidth] {images/MsRelations}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline. Smaller is better.}
        \label{fig:ms-relations}
        \vspace{-0.3cm}
    \end{figure}

@@

>>>>

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/MsRelations2}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline. Smaller is better.}
        \label{fig:ms-relations}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline, by workflow size. Smaller is better.}
        \label{fig:ms-relations-by-workflow}
        \vspace{-0.3cm}
    \end{figure}

    \paragraph{Memory Usage}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal}
        \caption{Memory usage by algorithm by workflow size. Includes invalid heft schedules}
        \label{fig:mem-usages}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal-onlyvalid}
        \caption{Memory usage by algorithm by workflow size. Includes only valid heft schedules}
        \label{fig:mem-usages-onlyvalid}
        \vspace{-0.3cm}
    \end{figure}

    \paragraph{Memory-constrained cluster}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/success-rates-tiny}
        \caption{Success ratey by algorithm by workflow size. Taller is better. }
        \label{fig:success-rates-tiny}
        \vspace{-0.3cm}
    \end{figure}

@@

    \subsubsection{Runtimes of the algorithm}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-logarithmic}
        \caption{Runtimes of the heuristics and the baseline. The y axis ist logarithmic.}
        \label{fig:runtimes-log}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-absolute}
        \caption{Runtimes of the heuristics and the baseline.}
        \label{fig:runtimes-abs}
        \vspace{-0.3cm}
    \end{figure}
